Master thesis

### 2017-07-13 10-Appendix4.Rmd
Thesis v1

To study resistance and resilience of ecosystem face to disturbance, highlighting the role of biodiversity, we decided to use TROLL model simulations [@Chave1999]. In order to get a finer study of simulations response, we need to assess first sensitivity of the TROLL model to different parameters. More particularly we need to assess the importance of functional traits to further better control functional diversities in simulations. We also need to assess sensitivity of the model to see rain constant because we assume it is one of the main factor of tree recruitments after disturbance in the model.

@@

To assess the sensitivity of TROLL model to species functionnal traits, we performed a sensitivity analysis by fixing species trait values to their mean. Each trait was tested independently. We reduce to a common mean traits with a correlation $r \geq 0.8$ (see figure \@ref(fig:A4corr)).

@@

Simulations were conducted on Intel Xeon(R) with 32 CPUs of 2.00GHz and 188.9 GB of memory. We assumed maturity of the forest after 500 years of regeneration [@Li] and computed simulation 100 years after a disturbance event of 40% intensity. Due to computer limitations we did not run replicate (besides it should be necessary to reduce simulation stochasticity). To assess ecosystem outputs sensitivity to studied parameters, we compared it to 100 replicates of control simulations with all parameters set to default values. Ecosystem outputs outside of the range of the control replicates values are significantly influenced by the studied parameter.

@@

Most of functional traits had a significant long term influence on ecosystem outputs (figure \@ref(fig:A4ftVar)). Only **seed volume** was always in the range of variation of control replicates. On the other hand, few functional traits influenced final ecosystem structure (figure \@ref(fig:A4ftStr)). Only specific maximum diameter **dmax** add higher diversity for greater orders implying better eveness in species distributions. Regarding functional composition, traits fixed to mean did not change other functional traits density distribution.

**ah-hmax** traits fixed to mean increased number of stems above 10 and above 30 cm dbh and basal area after disturbance (but not in long term) and did not affect aboveground biomass. Similarly, wood specific gravity **wsg** trait fixed to mean had exactly the same effect on number of stems above 10 and above 30 cm dbh and basal area after disturbance than **ah-hmax** but with a time lag ; and **wsg** also increased aboveground biomass. **dmax** trait fixed to mean slightly decreased number of stems above 10 and above 30 cm dbh over time while it increased basal area, aboveground biomass, and species eveness. Finally, leaf mass per area **LMA** trait fixed to mean only decreased number of stem above 10 cm dbh after ecosystem resilience to disturbance (approximately 50 years) but did not affect other ecosystem outputs.

@@

**ah-hmax** fixed to mean implied no high or low trees. Less high trees left space for more trees increasing number of stems in the ecosystem thus increasing basal area. Wood specific gravity **wsg** fixed to mean mainly increased wood density of light wood species. Globally higher wood density increased lifespan of individuals responsible for the time lag and the higher number of stems increasing basal area. **wsg** fiwed to mean also increased carbon capture by individuals, thus increasing aboveground biomass. Specific maximum diameter **dmax** fixed to mean decreased death rates. Decreased death rate diminished number of stems, expecially big ones thus increasing global basal area and abiveground biomass. **dmax** fixed to mean by keeping more small diameter stems also increased random selection of species increasing eveness in species distribution. Considering the high correlation between **ah** and **hmax** we could also keep only **hmax** (because of its more straightforward ecological meaning).

@@

Seedrain constant did not directly affect ecosystem global outputs over simulation post-disturbance time but have a major effect on species and functional composition and diversity. Reducing seedrain constant resulted in an ecosystem selecting few species increasing their abundance and functional dominance of their traits. Thus reduced seedrain constant greatly diminsihed eveness untill a decrease of total number of species for its lowest value.

>>>>

To study resistance and resilience of ecosystem face to disturbance, highlighting the role of biodiversity, we decided to use TROLL model simulations [@Chave1999]. In order to get a finer study of simulations response, we needed to assess sensitivity of the TROLL model to different parameters. More particularly we needed to assess the importance of functional traits to further better control functional diversities in simulations. We also needed to assess sensitivity of the model to see rain constant because we assumed it was one of the main factor of tree recruitments after disturbance in the model.

@@

To assess the sensitivity of TROLL model to species functionnal traits, we performed a sensitivity analysis by fixing species trait values to their mean. Each trait was tested independently. We reduced to a common mean traits with a correlation $r \geq 0.8$ (see figure \@ref(fig:A4corr)).

@@

Simulations were conducted on Intel Xeon(R) with 32 CPUs of 2.00GHz and 188.9 GB of memory. We assumed maturity of the forest after 500 years of regeneration [@Li] and computed simulation 100 years after a disturbance event of 40% intensity. Due to computer limitations we did not run replicates (besides it should be necessary to reduce simulation stochasticity). To assess ecosystem outputs sensitivity to studied parameters, we compared it to 100 replicates of control simulations with all parameters set to default values. Ecosystem outputs outside of the range of the control replicates values are significantly influenced by the studied parameter.

@@

Most of functional traits had a significant long term influence on ecosystem outputs (figure \@ref(fig:A4ftVar)). Only **seed volume** was always in the range of variation of control replicates. On the other hand, few functional traits influenced final ecosystem structure (figure \@ref(fig:A4ftStr)). Only specific maximum diameter **dmax** add higher diversity for greater orders implying better evenness in species distributions. Regarding functional composition, traits fixed to mean did not change other functional traits density distribution.

**ah-hmax** traits fixed to mean increased number of stems above 10 and above 30 cm dbh and basal area after disturbance (but not in long term) and did not affect aboveground biomass. Similarly, wood specific gravity **wsg** trait fixed to mean had exactly the same effect on number of stems above 10 and above 30 cm dbh and basal area after disturbance than **ah-hmax** but with a time lag ; and **wsg** also increased aboveground biomass. **dmax** trait fixed to mean slightly decreased number of stems above 10 and above 30 cm dbh over time while it increased basal area, aboveground biomass, and species evenness. Finally, leaf mass per area **LMA** trait fixed to mean only decreased number of stem above 10 cm dbh after ecosystem resilience to disturbance (approximately 50 years) but did not affect other ecosystem outputs.

@@

**ah-hmax** fixed to mean implied no high or low trees. Less high trees left space for more trees increasing number of stems in the ecosystem thus increasing basal area. Wood specific gravity **wsg** fixed to mean mainly increased wood density of light wood species. Globally higher wood density increased lifespan of individuals responsible for the time lag and the higher number of stems increasing basal area. **wsg** fiwed to mean also increased carbon capture by individuals, thus increasing aboveground biomass. Specific maximum diameter **dmax** fixed to mean decreased death rates. Decreased death rate diminished number of stems, expecially big ones thus increasing global basal area and abiveground biomass. **dmax** fixed to mean by keeping more small diameter stems also increased random selection of species increasing evenness in species distribution. Considering the high correlation between **ah** and **hmax** we could also keep only **hmax** (because of its more straightforward ecological meaning).

@@

Seedrain constant did not directly affect ecosystem global outputs over simulation post-disturbance time but have a major effect on species and functional composition and diversity. Reducing seedrain constant resulted in an ecosystem selecting few species increasing their abundance and functional dominance of their traits. Thus reduced seedrain constant greatly diminsihed evenness untill a decrease of total number of species for its lowest value.
